\chapter{Conclusions}\label{chap:conclusion}

The Heavy Photon Search (HPS) is a fixed target experiment located in Hall B at Jefferson Laboratory dedicated to searching for heavy photons (dark photons or $\aprime$s). Heavy photons are an extension of the Standard Model, arise from an additional $U(1)$ abelian gauge symmetry, and are connected to several models of dark matter. Heavy photons are particularly appealing to sub-GeV dark matter models that require a new comparably light mediator to achieve the current observed relic abundance of dark matter.

HPS utilizes a compact, forward acceptance spectrometer to search for heavy photons in the mass range $\sim 10 - 300$ MeV and kinetic mixing strength $\epsilon^2 \sim 10^{-5} - 10^{-10}$ that decay to $\epem$ pairs. For relatively large $\epsilon^2$, HPS can utilize a bump hunt in which a sharp resonance peak at the $\aprime$ mass appears over an invariant mass spectrum of QED tridents. For relatively small $\epsilon^2$, $\aprime$s have a finite livetime and a search for displaced vertices can be performed.

This dissertation focused on the results of the displaced vertex search for the 2016 Engineering Run. The peak sensitivity ruled out with 90\% confidence an $\aprime$-like model with an enhanced cross-section by a factor of 6.05 for a mass of 80.2 MeV and $\epsilon^2=2.12 \times 10^{-9}$. The luminosity from this dataset was, unfortunately, not enough to set a limit on the canonical $\aprime$ model; however, with $\sim$0.4 expected $\aprime$ events for a wide range of $\aprime$ parameter space, we are close to the sensitivity needed to observe a single $\aprime$ event. More importantly, the required background level to make this search possible (0.5 background events per independent mass bin) was achieved on a blinded data sample - a profound accomplishment for this dataset. This provides confidence that such a search with upgrades and increased luminosity is feasible and the latest projection with a dataset taken in 2019 shows sensitivity in new and highly motivated territory. In addition, a search for $\aprime$s that travel further downstream such that the daughter particles miss the full acceptance of the SVT was performed, and the feasibility of a displaced vertex search for models beyond the minimal $\aprime$ model was shown.